Statically Typed String Sanitation Inside a Python (Technical Report)

### 2014-12-14 sanitation-psp14/tr/strings_chapter.tex
Began texing plane work.

% bookmark1
\begin{trlem} \label{lem:inductive}
If $e \sreduces v$ and $e \mapsto e'$ then $e' \sreduces v$. 
\end{trlem}
\begin{proof}
By induction on the structure of e.
\begin{itemize}[label=$ $,itemsep=1ex]

@@

Third, if $e$ steps by L-E-AppAbs then $e = (\lambda x . e_3)(v_2) \mapsto [v_2 / x]e_3$.
By induction, $e = (\lambda x . e')v_2 \sreduces v$.
\end{itemize}
\end{proof}

@@

\begin{thm}[Semantic Correspondence]
If $\iots \mapsto^* \iota'$ then $\iota \sreduces \iota'$.
\end{thm}
\begin{proof}
By induction on the structure of $\iota$.

\begin{itemize}[label=$ $,itemsep=1ex]
\end{itemize}
\end{proof}

>>>>

% bookmark1
\begin{trlem} \label{lem:inductive}
If $e \sreduces v$ and $e \mapsto e'$ then $e' \sreduces v$. 
\end{trlem}
\begin{proof}
By induction on the structure of $e$.

@@

Third, if $e$ steps by L-E-AppAbs then $e = (\lambda x . e_3)(v_2) \mapsto [v_2 / x]e_3$.
By induction, $e = (\lambda x . e')v_2 \sreduces v$.

\item \todo{Other lambda cases}

\item \textbf{$s = \concat{e_1}{e_2}$}.
The only big-step rule that applies is S-E-Concat,
so $e \sreduces v$ where $v = \rstr{s_1s_2}$,
$e_1 \sreduces \rstr{s_1}$, and $e_2 \sreduces \rstr{s_2}$.

If $e_1 = \rstr{e_1}$ and $e_2 = \rstr{e_2}$ then $e \mapsto v$.
Otherwise either $e_1 \mapsto e_1'$ or else $e_2 \mapsto e_2'$.

In the former case, $e \mapsto \concat{e_1'}{e_2}$ by S-E-Concat-Left.
By induction, $e_1' \sreduces \rstr{s_1}$ and so 
$\concat{e_1'}{e_2} \sreduces v$.

In the latter case, $e \mapsto \concat{e_1}{e_2'}$ by S-E-Concat-Right.
By induction, $e_2 \sreduces e_2'$ form which it follows by S-E-Concat
that $\concat{e_1}{e_2'} \sreduces v$.

\item \textbf{$s = \rstrcase{e_1}{e_2}{x,y.e_3}$}.
\todo{finish...}

@@

\begin{thm}[Semantic Correspondence]
If $\iota \mapsto^* \iota'$ then $\iota \sreduces \iota'$.
\end{thm}
\begin{proof}
By induction on the structure of $\iota$.

\begin{itemize}[label=$ $,itemsep=1ex]
\item \todo{...}
\end{itemize}
\end{proof}
